How to compute the fusion product of MV cycles in type $A$

### 2021-06-07 draft.tex
Editted examples section

\section{Todolist}
\begin{itemize}
    \item Remove the TOC 
    \item Edit the intro 
    \item We are using the word [geometric] fusion just for the central fibre, we also have arithmetic fusion (aka multiplication in $\CC[N]$), and BD family: $X\geofu Y, b(X) \arfu b(Y), X \bdfamc Y\supset X\bdfamo Y$
    \item Which MVy paper to cite? 
    \item Super repetitive about lambdas and mus 
    \item Formatting could be bit better, e.g.\ some stuff goes outside the margin
    \item Fix section titles and other organizational seasoning  
    \item Fix numbering so that theorems, defs etc share a counter and are restarted by section 
    \item tableau of weight/filling? box of weight/filling? I prefer weight but don't mind filling 
    \item Recalling intersection multiplicity, checking that the definitions allow passing to open sets
    \item in examples put ideals of arithmetic fusion and their tableaux into tables; also split examples into 2 sections: $\GL_3$ and $\GL_4$; replace $Z_M$ by $Z(\tau)$ and $Z(\tau)$ by $\tau$; and let's use $A$ for matrices instead of $X$ to be consistent with rising action?
\end{itemize}

\section{Introduction}
\label{s:intro}
% 
%Throughout this paper (unless indicated otherwise) the base field is $\CC$, but it does not have to be?

The geometric Satake equivalence of Mirkovi\'c and Vilonen \cite{mirkovic2007geometric} provides an equivalence of categories between the category of spherical perverse sheaves in the affine Grassmannian of a reductive group $ G $ and the category of representations of its Langlands dual group $G^\vee$.  This foundational result provides a powerful tool to study representation theory using geometry.  In particular, under this equivalence, the Mirkovi\'c--Vilonen cycles in the affine Grassmannian of $ G $ index bases for irreducible representations of $ G^\vee $.  In this paper we work with $ G = \GL_m$ and identify $ G^\vee = \GL_m$ as well.

% The Mirkovi\'c--Vybornov isomorphism
In \cite{mirkovic2007quiver} (see also the recent sequel \cite{mirkovic2019comparison}) Mirkovi\'c and Vybornov provide a geometric version of symmetric and skew Howe $(\GL_m,\GL_N)$ dualities by relating Kazhdan--Lusztig slices in the affine Grassmannian of $\GL_m$ to slices in $N\times N$ nilpotent orbits on the one hand 
% conjugacy classes of nilpotent matrices 
and to Nakajima quiver varieties on the other hand.    The second author showed \cite{dthesis} that under the Mirkovi\'c-Vybornov isomorphism, the  Mirkovi\'c--Vilonen cycles are identified with certain varieties of matrices, called generalized orbital varieties.

@@

Essential to \cite{mirkovic2007geometric}, the Beilinson--Drinfeld Grassmannian is used to define a fusion product on the category of spherical perverse sheaves on the affine Grassmannian.  In \cite{anderson2003polytope}, Anderson used the Beilinson--Drinfeld Grassmannian to define a fusion of Mirkovi\'c--Vilonen cycles.  He conjectured that this fusion product matches the multiplication in the coordinate ring of the unipotent subgroup $ N \subset\GL_m$.  This conjecture was proven in \cite{baumann2019mirkovic}, where it was also established that the Mirkovi\'c--Vilonen cycles give a basis for $ \CC[N]$, which we call the MV basis. 
% 
%To quote from \cite{mirkovic2007geometric}:
%\begin{quotation}
%    However, we make crucial use of an idea of Drinfeld, going back to around 1990. He discovered an elegant way of obtaining the commutativity constraint by interpreting the convolution product of sheaves as a ``fusion'' product.
%\end{quotation}
%

Unfortunately, computing the fusion product of MV cycles using the BD Grassmannian is quite difficult, both computationally and conceptually.  A few such computations were done by Anderson-Kogan in \cite{anderson2006algebra} in a somewhat ad-hoc fashion.  Another perspective on these computations (using convolution Grassmannians) was recently studied by Baumann-Gaussent-Littelmann \cite{baumann2020bases}.

The purpose of this paper is to give a conceptually elementary way to compute this product by transferring it to a fusion product of generalized orbital varieties.  To do so, we use that the Mirkovic-Vybornov isomorphism extends to an isomorphism between families of slices in the Beilinson--Drinfeld and families of matrices with two eigenvalues. Our main result is the following.

\begin{maintheorem}
    Let $ Z, Z' $ be MV cycles.  The structure constants for the multiplication of $ b_Z b_{Z'}$ in $\CC[N]$ are equal to the intersection multiplicities in the fusion of the generalized orbital varieties corresponding to $ Z, Z'$.
\end{maintheorem}
% 
\jcom{I wanted to state a precise theorem, but it is not so easy without introducing a lot of notation.}

%One should care about the fusion product on bases \emoji{imp} \emoji{grin} \emoji{worried} \emoji{monocle-face} \emoji{skull} if one is interested in positivity!

An application of this result is to relate the cluster algebra structure in $\CC[N]$ to the MV basis. Cluster algebras were introduced by Fomin and Zelevinsky in \cite{fomin2002cluster1} and it was shown in \cite{berenstein2005cluster3} and \cite{geiss2007initial} that $\CC[N]$ has a natural cluster algebra structure.

This structure starts with an initial seed $\Sigma = ((x_1,\cdots,x_r),B)$ where $x_i \in \CC[N]$ and $B$ is some matrix. We obtain new variables through a process called mutation where for a mutable variable $x_i$, its mutation is the unique element $x_i^* \in \CC[N]$ such that $$x_ix_i^* = x_+ + x_-.$$
This equation is called an exchange relation and the terms $x_+$ and $x_-$ are some product in the $x_j$, $j\neq i$, that is determined by $B$. We then obtain a new seed $$\mu_i(\Sigma) = ((x_1,\cdots, x_{i-1}, x_i^*, x_{i+1},\cdots,x_r), \mu_i(B))$$ and can acquire possibly new variables through further mutations.

@@

It has been shown that the cluster monomials are in certain interesting bases such as the dual canonical basis \cite{lusztig1990canonicalbases}\cite{kang2018monoidal} and the dual semicanonical basis \cite{lusztig2000semicanonical}\cite{geiss2006rigid}. As these elements are defined in a combinatorial way, it allows efficient computation of several elements of these bases.

Although the MV basis and the above mentioned bases are in general different from each other \cite{baumann2019mirkovic}, it is believed that they at least all contain the cluster monomials, leading to the following conjecture.

@@

The conjecture is true in type $A_n$ with $n\leq 3$ as in these cases, the MV basis agrees with the dual semicanonical and dual canonical bases \cite{baumann2019mirkovic}. It has also been shown that cluster monomials supported on seeds satisfying a special condition are also in the MV basis \cite{baumann2020bases}. In addition, cluster variables coming from the initial seeds constructed in \cite{berenstein2005cluster3} are also in the MV basis \cite{kato2011polytopal}.

This leads to the following idea to show that the cluster variables are in the MV basis. Given a seed $((x_1,\cdots,x_r),B)$ with each of the $x_i$ in the MV basis, say corresponding to MV cycles $Z_i^*$, and an exchange relation $x_ix_i^* = x_+ + x_-$, it suffices to find an MV cycle $Z_i^*$ such that the fusion product of $Z_i$ and $Z_i^*$ gives $Z_+$ and $Z_-$, corresponding respectively to $x_+$ and $x_-$. In this case, we are able to conclude that $x_i^*$ is in the MV basis corresponding to the MV cycle $Z_i^*$. Inducting on mutation, we conclude that all cluster variables are in the MV basis.

We show in Section \ref{ss:GL4 examples} that this is indeed the case in type $A_3$ by directly computing each fusion product corresponding to an exchange relation.

@@

% $\CC[N]$ is a cluster algebra as shown in \cite[\S 4.3]{geiss2007initial} using \cite[Theorem~2.10]{berenstein2005cluster3}, and one of the main motivations for this paper is using fusion to check that certain cluster monomials are contained in the MV basis.
% % that are associated to exchange relations in $\CC[N]$ with its cluster algebra structure.

% \acom{Background on cluster:}
% In \cite{lusztig2000semicanonical}, Lusztig gives a geometric construction of a $\CC$-basis of $\cU\n$ the universal enveloping algebra of the Lie algebra of $N$, called the semicanonical basis. This becomes the dual semicanonical basis of the graded dual of $\cU\n$ which is isomorphic (as a Hopf algebra) to $\CC[N]$. 
% Geiss, Leclerc \& Schroer prove that certain cluster monomials are contained in Lusztig's (dual) semicanonical basis \cite[Theorem~2.8(3)]{geiss2006rigid}.

@@

\section{Players}
\label{s:players}
\subsection{Rings and discs}
\label{ss:rings}
Set $\cO = \cO_0 = \CC\xt$ and $\cK = \cK_0 = \CC\xT$.
% TODO: I rearranged this sentence, because starting it with 'for any other' presupposes we have introduced s 
%  For any other 
We will also consider $\cO_s = \CC\xt[t-s]$ and its fraction field $\cK_s=\CC\xT[t-s]$, for any 
$ s \in \CC\setminus\{0\} $, as well as $ \Oinf = \CC\xt[t^{-1}] $ and $\Kinf = \CC\xT[t^{-1}]$. For any point $ s \in \PP = \PP^1$, 
% TODO: Identifying $s\in\CC$ and the line $s\in\PP$ containing it right?
$ \cO_s$ is the completion of the local ring $ \mathcal O_{\PP, s} $ and thus the formal spectrum of $ \cO_s$ is the formal neighbourhood $ D_s$ of $ s $ (also called the formal disc centered at $ s$).  Similarly the formal spectrum of the field $\cK_s$ is the deleted formal neighbourhood (or punctured disc), denoted $ D_s^\times$.

@@

\subsection{Affine Grassmannians} 
\label{ss:affgrs}
% To map thick Gr to C is to map a lattice to the points where it isn't trivialzable; doesn't make sense to ask for poles 
% G(C(t))/G(C[t]) for example lives over the Ran space, finitely many eigenvalues; positive part of thick contains this guy as image 
%Set $\AA = \AA^1$ viewed as the subset $\PP\setminus \{\infty\}$ of $\PP$. Let $\Vtriv$ denote the trivial rank $ m $ vector bundle. 
% 
We now define various versions of the affine Grassmannian which will play important roles in this paper. 
% 
Each definition is made group-theoretically and then restated as a moduli space of vector bundles and as a moduli space of lattices.
% 
We also sketch how to pass between descriptions.

@@

\acom{Comment why the above doesn't make sense for $\mu$ not dominant?}
\jcom{It does make sense when $ \mu $ is not dominant.  The reason for restricting to dominant $ \mu $ is so that $ S^\mu \subset \cW^\mu$.  I agree that we should mention this, but I'm not sure where.} \acom{Yes, sorry. We could say it here?} 
% 
% \acom{First lattice description that doesn't come for free?}
% 
% \acom{que est-ce?} \jcom{It's not very relevant for this paper.  Here is an explanation: every vector bundle on $\PP$ (or maybe any curve) has a special filtration called the HN--filtration; it is a partial flag of subbundles of type determined by $ \mu$.  We require that $ \varphi$ takes this filtration to the standard partial flag at the fibre over $ \infty$.  Maybe ``preserves'' is not the best word above.}
% A: Ok thanks!
% 
\begin{definition} 
\label{def:inftyorbit}
    The \new{semi-infinite orbit} $ S^\mu = N_-(\cK)t^\mu \subset \Gr $
\end{definition}
% \acom{and its closure?}
% \jcom{I don't think that we use the closure in this paper, do we?}
% \acom{No you are right we do not.}
\begin{definition} 
\label{def:inftyorbitfam}
    The \new{family of two semi-infinite orbits} 
 $S^{\mu', \mu''}_{0,\AA} \subset \Grbd$
 which we define to have fibres $ S^{\mu', \mu''}_{0,s} := \theta_s^{-1}( S^{\mu'}\times S^{\mu''}) $ for $ s \ne 0$ and fibre $ \theta_0^{-1}(S^{\mu})$ over $ s = 0 $.
\end{definition}
%Note that since $ S^{\mu}$ is not closed, it is not true that $S^{\mu', \mu''}_{0,\AA} = S^{\mu'} \ast_\AA S^{\mu''}$.
% 
%\acom{Commented out fusion part for now. Unsure about defining it as the family whose 0 fibre is $S^{\mu' + \mu''}$ and whose generic fibre is $S^{\mu'}\times S^{\mu''}$ up to $\tau$. Baumann--Riche consider the attracting set of $C_\mu = \sqcup_{\mu' + \mu'' = \mu } m(\tilde C_{\mu',\mu''})$ where $\tilde C_{\mu',\mu''}$ is a connected component of fixed points in $\Grbd\tilde\times\Grbd$. Maybe we can consider the attracting set of just one of these?}
% 
We can also describe the fibres as orbits
$$
 S^{\mu', \mu''}_{0,s} = 
    N_-(\CC[t, t^{-1}, (t-s)^{-1}])t^{\mu'} (t-s)^{\mu''} \subset G(\CC[t,t^{-1}, (t-s)^{-1}]) / G(\CC[t]) \,. % \G(\CC[t])
$$
See \cite[Section~5.2]{baumann2020bases} for further details where this fibre is also described as the attracting locus for a $\Cx$ action.

@@

\jcom{Following Anne's comment above about dominant $ \mu$, I decided to move this result here.}

@@

\section{Rising Action}
\label{s:theproblem}

Throughout this section, we continue our notation of the previous sections. So $ \lambda, \lambda', \lambda''$ denote dominant effective coweights for $ \GL_m$, with $ \lambda' + \lambda'' = \lambda$.  Also $ \mu, \mu', \mu''$ are effective coweights with $ \mu = \mu' + \mu''$ and we assume that $ \mu$ is dominant.

@@

% 
\section{Climax}
\label{s:climax}
Throughout this section, we continue our notation of the previous sections. So $ \lambda, \lambda', \lambda''$ denote dominant effective coweights for $ \GL_m$, with $ \lambda' + \lambda'' = \lambda$.  Also $ \mu, \mu', \mu''$ are effective coweights with $ \mu = \mu' + \mu''$ and we assume that $ \mu$ is dominant.

@@

\section{\sout{Falling Action}} % Resolution  
\label{se:falling}
\subsection{MV cycles}
%Let $Q_+$ denote the $\ZZ_{\ge 0}$-span of the positive coroots. 
%Recall the \new{dominance order} on $\ZZ^m$ defined by declaring that $\mu\le\lambda$ if $\lambda - \mu\in Q_+$ for any $\lambda,\mu$.

@@

The following result is closely related to  Theorem 5.4.3. from \cite{dthesis}. It is also closely related to the description of MV cycles in terms of Kostant data obtained by Anderson--Kogan \cite{anderson2004mirkovic} (see Section 9 in \cite{kamnitzer2010mirkovic}).  
We remeark that a different map from Young tableaux to MV cycles was obtained by Gaussent--Littelmann--Nguyen \cite[Theorem 2]{gaussent2013knuth}; we are not certain of the relation with our construction.

@@

By \cite[Prop.\ 4.5.4]{dthesis}, $ \mathring X(\tau) $ has a unique irreducible component of dimension $ \rho(\lambda - \mu)$.  We write $ X(\tau)$ for the closure of this component.  It is an irreducible component of $ \overline{\OO}^\lambda \cap \TT_\mu \cap \n$ and will be called a \new{generalized orbital variety}.
% 
% \jcom{We should give a more specific citation to \cite{dthesis} here and below.  Also, throughout this paper, we should either cite your paper or your thesis, but not both (unless there is a very good reason to do so).  I reorganized this section a bit.  Feel free to add a bit more exposition.}
% \acom{Just posted to arXiv. Will re-ref shortly. Also made citation more specific.}
% 
In fact, these are all the generalized orbital varieties:
\begin{theorem}(\cite[Theorem~4.8.2]{dthesis})
    \label{pr:govsasirrecs}
    $\{{X(\tau)} : \tau\in YT(\lambda)_\mu\}$ is a complete set of irreducible components of $\overline{\OO}^\lambda\cap\TT_\mu\cap\n$. 
\end{theorem}
%

@@

\acom{So far we have been saying ``coweight'' $\lambda$, etc. We could say coweight for $t^\lambda$ and weight for $\lambda$ starting now?}
% \acom{Also, maybe add a warning that some of the theorems we rely on hold more generally? Like the MV basis theorem..} \jcom{I don't think that is necessary.}

>>>>

\section{Todolist}
\begin{itemize}
    \item Remove the TOC 
    \item a shorthand: in examples, instead of writing $Z(\tau)$ for the MV cycle corresponding to the tableau $\tau$ we will only the tableau $\tau$!
    \item our $B(\infty) \to B(\lambda)$ does not match that of Claxton--Tingley or Hong--Lee but discussing how the two are related might be irrelevant since we don't worry about the crystal structure on MV cycles anyway (let alone investigate possible compatibility with the crystal structure on SSYT given $\tau\mapsto Z(\tau)$); \acom{perhaps we could mention that we don't know if this map is compatible with crystal structures} (but suspect there is a way of making it so); 
    \item Edit the intro 
    \item We are using the word [geometric] fusion just for the central fibre, we also have arithmetic fusion (aka multiplication in $\CC[N]$), and BD family: $X\geofu Y, b(X) \arfu b(Y), X \bdfamc Y\supset X\bdfamo Y$
    \item[\checkmark] Which MVy paper to cite? Both
    \item Super repetitive about lambdas and mus 
    \item Formatting could be bit better, e.g.\ some stuff goes outside the margin
    \item Fix section titles and other organizational seasoning  
    \item Fix numbering so that theorems, defs etc share a counter and are restarted by section 
    \item tableau of weight/filling? box of weight/filling? I prefer weight but don't mind filling 
    \item Recalling intersection multiplicity, checking that the definitions allow passing to open sets
    \item[\checkmark] in examples put ideals of arithmetic fusion and their tableaux into tables; also split examples into 2 sections: $\GL_3$ and $\GL_4$; replace $Z_M$ by $Z(\tau)$ and $Z(\tau)$ by $\tau$; and let's use $A$ for matrices instead of $X$ to be consistent with rising action?
\end{itemize}

\section{Introduction}
\label{s:intro}
% 
%Throughout this paper (unless indicated otherwise) the base field is $\CC$, but it does not have to be?  
\subsection{Geometric Satake and Mirkovic--Vilonen cycles}
The geometric Satake equivalence of Mirkovi\'c and Vilonen \cite{mirkovic2007geometric} provides an equivalence of categories between the category of spherical perverse sheaves in the affine Grassmannian of a reductive group $ G $ and the category of representations of its Langlands dual group $G^\vee$.  This foundational result provides a powerful tool to study representation theory using geometry.  In particular, under this equivalence, the Mirkovi\'c--Vilonen cycles in the affine Grassmannian of $ G $ index bases for irreducible representations of $ G^\vee $.  In this paper we work with $ G = \GL_m$ and identify $ G^\vee = \GL_m$ as well.

% The Mirkovi\'c--Vybornov isomorphism
In \cite{mirkovic2007quiver} (see also the recent sequel \cite{mirkovic2019comparison}) Mirkovi\'c and Vybornov provide a geometric version of symmetric and skew Howe $(\GL_m,\GL_N)$ dualities.  They relate Kazhdan--Lusztig slices in the affine Grassmannian of $\GL_m$ to slices in $N\times N$ nilpotent orbits on the one hand, 
% conjugacy classes of nilpotent matrices 
and to Nakajima quiver varieties on the other hand.    The second author \cite{dthesis} showed  that under the Mirkovi\'c-Vybornov isomorphism, the MV cycles are identified with certain varieties of matrices, called generalized orbital varieties.

@@

Essential to \cite{mirkovic2007geometric}, the Beilinson--Drinfeld Grassmannian is used to define a fusion product on the category of spherical perverse sheaves on the affine Grassmannian.  In \cite{anderson2003polytope}, Anderson used the Beilinson--Drinfeld Grassmannian to define a fusion of Mirkovi\'c--Vilonen cycles.  He constructed a family where the general fibre is a Cartesian product of two MV cycles, and the special fibre, called the fusion, is a (non-reduced) union of MV cycles.  Anderson conjectured that this fusion product matches the multiplication in the coordinate ring of the unipotent subgroup $ N \subset\GL_m$.  This conjecture was proven in \cite{baumann2019mirkovic}, where it was also established that the MV cycles give a basis for $ \CC[N]$.
% 
%To quote from \cite{mirkovic2007geometric}:
%\begin{quotation}
%    However, we make crucial use of an idea of Drinfeld, going back to around 1990. He discovered an elegant way of obtaining the commutativity constraint by interpreting the convolution product of sheaves as a ``fusion'' product.
%\end{quotation}
%

\subsection{Fusion using generalized orbital varieties}
% \acom{imho, fortune has nothing to do with it :)}
% Unfortunately, c
Computing the fusion product of MV cycles using the BD Grassmannian is quite difficult, both computationally and conceptually.  A few such computations were done by Anderson-Kogan in \cite{anderson2006algebra} in a somewhat ad-hoc fashion.  Another perspective on these computations (using convolution Grassmannians) was recently studied by Baumann, Gaussent \& Littelmann \cite{baumann2020bases}.

The purpose of this paper is to give a conceptually elementary way to compute this product by transferring it to a fusion product of generalized orbital varieties.  To do so, we use that the Mirkovic-Vybornov isomorphism extends to an isomorphism between families of slices in the Beilinson--Drinfeld and families of slices of matrices with two eigenvalues. Our main result is the following.

\begin{theorem}
    Let $ Z, Z' $ be MV cycles.  The structure constants for the multiplication $ b_Z b_{Z'}$ in $\CC[N]$ are equal to the intersection multiplicities in the fusion of the generalized orbital varieties corresponding to $ Z, Z'$.
\end{theorem}
% 
\jcom{I wanted to state a precise theorem, but it is not so easy without introducing a lot of notation.}
\acom{Are you ok with the 'maintheorem' environemnt?}

Since these generalized orbital varieties are subschemes of affine spaces of matrices defined by certain rank conditions, the fusion of generalized orbital varieties can be computed by elementary commutative algebra.

%One should care about the fusion product on bases \emoji{imp} \emoji{grin} \emoji{worried} \emoji{monocle-face} \emoji{skull} if one is interested in positivity!
\subsection{Cluster algebras and MV cycles}
One motivation for computing products of MV basis elements is to relate the cluster algebra structure on $\CC[N]$ to the MV basis. Cluster algebras were introduced by Fomin and Zelevinsky in \cite{fomin2002cluster1} and it was shown in \cite{geiss2007initial}, using the construction of \cite{berenstein2005cluster3}, that $\CC[N]$ has a natural cluster algebra structure. 
\acom{As a reader I am confused - did both of them show it independently? Can I go to either source to find out how this works? I suggest ``in \cite[\S 4.3]{geiss2007initial} using \cite[Theorem~2.10]{berenstein2005cluster3}''} \rcom{I agree with the suggestion.}

This structure starts with an initial seed $\Sigma = ((x_1,\dots,x_r),B)$, where $x_i \in \CC[N]$, $B$ is a certain matrix, and $ r = m(m-1)/2$ ($=\#\Delta_+$). We obtain new variables through a process called mutation where for a mutable variable $x_i$, its mutation is the unique element $x_i^* \in \CC[N]$ such that $$x_ix_i^* = x_+ + x_-.$$
This equation is called an exchange relation and the terms $x_+$ and $x_-$ are certain monomials in the $x_j$, $j\neq i$,  determined by $B$. 
%We then obtain a new seed $$\mu_i(\Sigma) = ((x_1,\cdots, x_{i-1}, x_i^*, x_{i+1},\cdots,x_r), \mu_i(B))$$ and can acquire possibly new variables through further mutations.

@@

\acom{It would be nice to add a line to set up this paragraph. Else the canonical bases come out of nowhere? Like ``There is another nice structure on $\CC[N]$, that of a \new{perfect basis} introduced by/studied by...; and heaps of work (or just the following two sources) suggests that the two structures are inextricably linked.'' Because it's a paper and not a talk.}
\rcom{Something along these lines?}
There are two well-known bases of $\CC[N]$ whose relationship with the cluster structure has been studied heavily: the dual canonical basis \cite{lusztig1990canonicalbases} and the dual semicanonical basis \cite{lusztig2000semicanonical}.
Kang, Kashiwara, Kim \& Oh showed that all cluster monomials are contained in the dual canonical basis \cite{kang2018monoidal} while Gei\ss, Leclerc, \& Schr\"oer proved that they are all contained in the dual semicanonical basis \cite[Theorem~2.8(3)]{geiss2006rigid}.
% 
%It has been shown that the cluster monomials are in certain interesting bases such as the dual canonical basis \cite{lusztig1990canonicalbases}\cite{kang2018monoidal} and the dual semicanonical basis \cite{lusztig2000semicanonical}\cite{geiss2006rigid}. As these elements are defined in a combinatorial way, it allows efficient computation of several elements of these bases.
% 
%\acom{Re: above paragraph, I actually dug up the precise references in rewriting this so maybe we can preserve that...}
%a geometric construction of a $\CC$-basis of $\cU\n$ the universal enveloping algebra of the Lie algebra of $N$, called the semicanonical basis. This becomes the dual semicanonical basis of the graded dual of $\cU\n$ which is isomorphic (as a Hopf algebra) to $\CC[N]$. 
%Geiss, Leclerc \& Schroer prove that certain cluster monomials are contained in Lusztig's (dual) semicanonical basis \cite[Theorem~2.8(3)]{geiss2006rigid}.}
%

Although the MV basis differs from these bases (at least at the Kashiwara--Saito counterexample \cite[Appendix]{baumann2019mirkovic}), they are all examples of biperfect bases \cite{baumann2019mirkovic}.
% and the above mentioned bases are in general different from each other \cite{baumann2019mirkovic}, 
\acom{can we say something other than ``it is believed'', like ``Evidence/calculations/etc.\ suggests''}
%along with evidence suggests that they all contain the cluster monomials, leading to the following conjecture.
This then leads to the following conjecture.

@@

The conjecture is true in type $A_n$ for $n\leq 3$ 
% as the MV basis and the dual semicanonical basis agree in these cases 
since in these cases $\CC[N]$ has a unique biperfect basis (C.f.\ \cite{baumann2019mirkovic}).
% 
More generally, cluster monomials supported on seeds satisfying certain extra conditions were shown to be in the MV basis in \cite{baumann2020bases}. 
Also, cluster variables coming from the initial seeds constructed in \cite{berenstein2005cluster3} are in the MV basis \cite{baumann2019mirkovic}.

% \acom{Re the above paragraph, I like how it was: It has been shown in \cite{kato2011polytopal} that for initial seeds $(x_1, \dots, x_r)$ obtained from a reduced expression of the longest word in the Weyl group for $G$, each $x_i$ is in the MV basis as these correspond to generalized minors introduced in \cite{berenstein2005cluster3} created in \cite{geiss2007initial} for the dual semicanonical basis. If the reduced expression satisfies a special condition, then the cluster monomials in the initial seed are also in the MV basis \cite{baumann2020bases}.}

%This leads to the following idea to show that the cluster variables are in the MV basis. Given a seed $((x_1,\cdots,x_r),B)$ with each of the $x_i$ in the MV basis, say corresponding to MV cycles $Z_i^*$, and an exchange relation $x_ix_i^* = x_+ + x_-$, it suffices to find an MV cycle $Z_i^*$ such that the fusion product of $Z_i$ and $Z_i^*$ gives $Z_+$ and $Z_-$, corresponding respectively to $x_+$ and $x_-$. In this case, we are able to conclude that $x_i^*$ is in the MV basis corresponding to the MV cycle $Z_i^*$. Inducting on mutation, we conclude that all cluster variables are in the MV basis.

In particular, we hope that each exchange relation can be realized using the fusion of MV cycles. If so, we are then able to conclude that all cluster variables are in the MV basis. We show in Section \ref{ss:GL4 examples} that this is indeed the case in type $A_3$, by directly computing each fusion product corresponding to an exchange relation.

@@

% $\CC[N]$ is a cluster algebra as shown in \cite[\S 4.3]{geiss2007initial} using \cite[Theorem~2.10]{berenstein2005cluster3}, and one of the main motivations for this paper is using fusion to check that certain cluster monomials are contained in the MV basis.
% that are associated to exchange relations in $\CC[N]$ with its cluster algebra structure.

% \acom{Background on cluster:}

@@

\section{Supporting Cast}
\label{s:players}
\subsection{Rings and discs}
\label{ss:rings}
Set $\cO = \cO_0 = \CC\xt$ and $\cK = \cK_0 = \CC\xT$.
% TODO: I rearranged this sentence, because starting it with 'for any other' presupposes we have introduced s 
%  For any other 
We will also consider $\cO_s = \CC\xt[t-s]$ and its fraction field $\cK_s=\CC\xT[t-s]$, for any 
$ s \in \CC\setminus\{0\} $, as well as $ \Oinf = \CC\xt[t^{-1}] $ and $\Kinf = \CC\xT[t^{-1}]$. For any point $ s \in \PP = \PP^1$, 
% TODO: Identifying $s\in\CC$ and the line $s\in\PP$ containing it right?
$ \cO_s$ is the completion of the local ring $ \mathcal O_{\PP, s} $ and thus the formal spectrum of $ \cO_s$ is the formal neighbourhood $ D_s$ of $ s $ (also called the formal disc centered at $ s$).  Similarly the formal spectrum of the field $\cK_s$ is the deleted formal neighbourhood (or punctured disc), denoted $ D_s^\times$.

@@

\section{Affine Grassmannians} 
\label{s:affgrs}
% To map thick Gr to C is to map a lattice to the points where it isn't trivialzable; doesn't make sense to ask for poles 
% G(C(t))/G(C[t]) for example lives over the Ran space, finitely many eigenvalues; positive part of thick contains this guy as image 
%Set $\AA = \AA^1$ viewed as the subset $\PP\setminus \{\infty\}$ of $\PP$. Let $\Vtriv$ denote the trivial rank $ m $ vector bundle. 
% 
We now define various versions of the affine Grassmannian which will play important roles in this paper. 
% 
Each definition is made group-theoretically and then restated as a moduli space of vector bundles and as a moduli space of lattices.
% 
We also sketch how to pass between descriptions.

@@

% \acom{Comment why the above doesn't make sense for $\mu$ not dominant?}
% \jcom{It does make sense when $ \mu $ is not dominant.  The reason for restricting to dominant $ \mu $ is so that $ S^\mu \subset \cW^\mu$.  I agree that we should mention this, but I'm not sure where.} \acom{Yes, sorry. We could say it here?} 
% 
% \acom{First lattice description that doesn't come for free?}
% 
% \acom{que est-ce?} \jcom{It's not very relevant for this paper.  Here is an explanation: every vector bundle on $\PP$ (or maybe any curve) has a special filtration called the HN--filtration; it is a partial flag of subbundles of type determined by $ \mu$.  We require that $ \varphi$ takes this filtration to the standard partial flag at the fibre over $ \infty$.  Maybe ``preserves'' is not the best word above.}
% A: Ok thanks!
% 
\begin{definition} 
\label{def:inftyorbit}
    The \new{semi-infinite orbit} $ S^\mu = N_-(\cK)t^\mu \subset \Gr $
\end{definition}
% \acom{and its closure?}
% \jcom{I don't think that we use the closure in this paper, do we?}
% \acom{No you are right we do not.}
\begin{definition} 
\label{def:inftyorbitfam}
    The \new{family of two semi-infinite orbits} 
 $S^{\mu', \mu''}_{0,\AA} \subset \Grbd$
 which we define to have fibres $ S^{\mu', \mu''}_{0,s} := \theta_s^{-1}( S^{\mu'}\times S^{\mu''}) $ for $ s \ne 0$ and fibre $ \theta_0^{-1}(S^{\mu})$ over $ s = 0 $.
\end{definition}
%Note that since $ S^{\mu}$ is not closed, it is not true that $S^{\mu', \mu''}_{0,\AA} = S^{\mu'} \ast_\AA S^{\mu''}$.
% 
%\acom{Commented out fusion part for now. Unsure about defining it as the family whose 0 fibre is $S^{\mu' + \mu''}$ and whose generic fibre is $S^{\mu'}\times S^{\mu''}$ up to $\tau$. Baumann--Riche consider the attracting set of $C_\mu = \sqcup_{\mu' + \mu'' = \mu } m(\tilde C_{\mu',\mu''})$ where $\tilde C_{\mu',\mu''}$ is a connected component of fixed points in $\Grbd\tilde\times\Grbd$. Maybe we can consider the attracting set of just one of these?}
% 
We can also describe the fibres as orbits
$$
 S^{\mu', \mu''}_{0,s} = 
    N_-(\CC[t, t^{-1}, (t-s)^{-1}])t^{\mu'} (t-s)^{\mu''} \subset G(\CC[t,t^{-1}, (t-s)^{-1}]) / G(\CC[t]) \,. % \G(\CC[t])
$$
See \cite[Section~5.2]{baumann2020bases} for further details where this fibre is also described as the attracting locus for a $\Cx$ action.

@@

% \jcom{Following Anne's comment above about dominant $ \mu$, I decided to move this result here.}
% \acom{The observation is verified in Anne's thesis}

@@

\section{Rising Action} 
\label{s:rising}

\subsection{Linear Operators from Affine Grassmannians}
\label{s:latticefacts}
% 
Throughout this section, we continue our notation of the previous sections. So $ \lambda, \lambda', \lambda''$ denote dominant effective coweights for $ \GL_m$, with $ \lambda' + \lambda'' = \lambda$.  Also $ \mu, \mu', \mu''$ are effective coweights with $ \mu = \mu' + \mu''$ and we assume that $ \mu$ is dominant.

@@

% 
% \section{Climax}
% \label{s:climax}
\subsection{Matrices from Affine Grassmannians}
\label{ss:mvyisos}
% 
Throughout this section, we continue our notation of the previous sections. So $ \lambda, \lambda', \lambda''$ denote dominant effective coweights for $ \GL_m$, with $ \lambda' + \lambda'' = \lambda$.  Also $ \mu, \mu', \mu''$ are effective coweights with $ \mu = \mu' + \mu''$ and we assume that $ \mu$ is dominant.

@@

% \section{\sout{Falling Action}} % Resolution  
% \label{se:falling}
\section{Climax}
\label{s:climax}
\subsection{MV cycles}
\label{ss:mvcs}
%Let $Q_+$ denote the $\ZZ_{\ge 0}$-span of the positive coroots. 
%Recall the \new{dominance order} on $\ZZ^m$ defined by declaring that $\mu\le\lambda$ if $\lambda - \mu\in Q_+$ for any $\lambda,\mu$.

@@

The following result is closely related to  Theorem 5.4.3. from \cite{dthesis}. It is also closely related to the description of MV cycles in terms of Kostant data obtained by Anderson--Kogan \cite{anderson2004mirkovic} (see Section 9 in \cite{kamnitzer2010mirkovic}).  
We remark that a different map from Young tableaux to MV cycles was obtained by Gaussent--Littelmann--Nguyen \cite[Theorem 2]{gaussent2013knuth}; we are not certain of the relation with our construction.

@@

By \cite[Prop.\ 4.5.4]{dthesis}, $ \mathring X(\tau) $ has a unique irreducible component of dimension $ \rho(\lambda - \mu)$.  We write $ X(\tau)$ for the closure of this component.  It is an irreducible component of $ \overline{\OO}^\lambda \cap \TT_\mu \cap \n$ and will be called a \new{generalized orbital variety}.
% 
% \jcom{We should give a more specific citation to \cite{dthesis} here and below.  Also, throughout this paper, we should either cite your paper or your thesis, but not both (unless there is a very good reason to do so).  I reorganized this section a bit.  Feel free to add a bit more exposition.}
% \acom{Just posted to arXiv. Will re-ref shortly. Also made citation more specific.}
% 
% In fact, these are all the generalized orbital varieties:
\begin{theorem}(\cite[Theorem~4.8.2]{dthesis})
    \label{pr:govsasirrecs}
    $\{{X(\tau)} : \tau\in YT(\lambda)_\mu\}$ is a complete set of irreducible components of $\overline{\OO}^\lambda\cap\TT_\mu\cap\n$. 
\end{theorem}
%

@@

% \acom{So far we have been saying ``coweight'' $\lambda$, etc. We could say coweight for $t^\lambda$ and weight for $\lambda$ starting now?}
% \acom{Also, maybe add a warning that some of the theorems we rely on hold more generally? Like the MV basis theorem..} \jcom{I don't think that is necessary.}
